---
title: "Diagnostic Plots - Secondary Predictor Models"
subtitle: "The effects of muscle length during resistance training on regional hypertrophy adaptations: A systematic review and meta-analysis"
author: "Dorian Varovic, Milo Wolf, Brad J. Schoenfeld, James Steele, Jozo Grgic Pavle Mikulic"
format:
  pdf:
    documentclass: report
    toc: false
    number-sections: false
    highlight-style: github
    fig-width: 10
    fig-height: 10
---
```{r}
#| message: false
#| warning: false
#| echo: false
#| include: false
targets::tar_config_set(store = here::here('_targets'))
```

# Standardised Mean Difference Models

## Upper vs Lower Body

### $\hat{R}$

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(rhat_upper_lower_model_SMD)

rhat_upper_lower_model_SMD 

```

### Trace plots

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(trace_plot_upper_lower_model_SMD)

trace_plot_upper_lower_model_SMD

```

### Posterior predictive check

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(pp_check_upper_lower_model_SMD)

pp_check_upper_lower_model_SMD

```

## Muscle Group

### $\hat{R}$

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(rhat_muscle_model_SMD)

rhat_muscle_model_SMD 

```

### Trace plots

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(trace_plot_muscle_model_SMD)

trace_plot_muscle_model_SMD

```

### Posterior predictive check

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(pp_check_muscle_model_SMD)

pp_check_muscle_model_SMD

```

## Muscle Action

### $\hat{R}$

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(rhat_muscle_action_model_SMD)

rhat_muscle_action_model_SMD 

```

### Trace plots

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(trace_plot_muscle_action_model_SMD)

trace_plot_muscle_action_model_SMD

```

### Posterior predictive check

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(pp_check_muscle_action_model_SMD)

pp_check_muscle_action_model_SMD

```

## Method of Manipulating Muscle Length

### $\hat{R}$

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(rhat_muscle_length_manipulation_model_SMD)

rhat_muscle_length_manipulation_model_SMD 

```

### Trace plots

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(trace_plot_muscle_length_manipulation_model_SMD)

trace_plot_muscle_length_manipulation_model_SMD

```

### Posterior predictive check

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(pp_check_muscle_length_manipulation_model_SMD)

pp_check_muscle_length_manipulation_model_SMD

```

# Log Response Ratio Models

## Upper vs Lower Body

### $\hat{R}$

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(rhat_upper_lower_model_lnRR)

rhat_upper_lower_model_lnRR 

```

### Trace plots

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(trace_plot_upper_lower_model_lnRR)

trace_plot_upper_lower_model_lnRR

```

### Posterior predictive check

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(pp_check_upper_lower_model_lnRR)

pp_check_upper_lower_model_lnRR

```

## Muscle Group

### $\hat{R}$

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(rhat_muscle_model_lnRR)

rhat_muscle_model_lnRR 

```

### Trace plots

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(trace_plot_muscle_model_lnRR)

trace_plot_muscle_model_lnRR

```

### Posterior predictive check

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(pp_check_muscle_model_lnRR)

pp_check_muscle_model_lnRR

```

## Muscle Action

### $\hat{R}$

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(rhat_muscle_action_model_lnRR)

rhat_muscle_action_model_lnRR 

```

### Trace plots

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(trace_plot_muscle_action_model_lnRR)

trace_plot_muscle_action_model_lnRR

```

### Posterior predictive check

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(pp_check_muscle_action_model_lnRR)

pp_check_muscle_action_model_lnRR

```

## Method of Manipulating Muscle Length

### $\hat{R}$

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(rhat_muscle_length_manipulation_model_lnRR)

rhat_muscle_length_manipulation_model_lnRR 

```

### Trace plots

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(trace_plot_muscle_length_manipulation_model_lnRR)

trace_plot_muscle_length_manipulation_model_lnRR

```

### Posterior predictive check

```{r}
#| message: false
#| warning: false
#| echo: false

targets::tar_load(pp_check_muscle_length_manipulation_model_lnRR)

pp_check_muscle_length_manipulation_model_lnRR

```





